%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Amazon Connect Incident Response} $|$ \emph{Lambda, Amazon Connect, DynamoDB, SNS, Python}}{}
          \resumeItemListStart
            \resumeItem{An automated incident response system built with Amazon Connect that triggers escalation calls when alerts are received}
            \resumeItem{The system uses AWS Lambda to orchestrate outbound calls, with automatic escalation to secondary contacts if the first contact doesn't respond}
            \resumeItem{Features include call status monitoring, DynamoDB logging, and SNS integration for alert management.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Endless Jumper} $|$ \emph{Python, Pygame, Amazon Q}}{}
          \resumeItemListStart
            \resumeItem{A fun endless runner game built in just 2 hours using Amazon Q AI assistant}
            \resumeItem{Features include power-ups, increasing difficulty, and smooth gameplay mechanics}
            \resumeItem{The game demonstrates rapid prototyping and AI-assisted development.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Alibaba Cloud: DataV Webinar} $|$ \emph{DataV, Alibaba Cloud}}{}
          \resumeItemListStart
            \resumeItem{A webinar where I was invited to speak about utilizing Alibaba Cloud's DataV for real-time data visualization and monitoring.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Slack Bot} $|$ \emph{Python, Slack API, AWS}}{}
          \resumeItemListStart
            \resumeItem{A custom Slack bot built to automate workspace tasks and streamline team workflows using Python, Slack API, and AWS services.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Webcam Test} $|$ \emph{HTML, JavaScript, WebRTC}}{}
          \resumeItemListStart
            \resumeItem{A static webpage designed for testing your webcam before going live, ensuring you look great before presenting yourself to the world.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Portfolio Website} $|$ \emph{TypeScript, Vite, HTML, CSS, JavaScript}}{}
          \resumeItemListStart
            \resumeItem{A dynamic personal portfolio website built with TypeScript, Vite, and modern web technologies}
            \resumeItem{Features include interactive timeline, project showcase, and dynamic content loading from JSON configuration.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{ShareShed} $|$ \emph{Python, Django, HTML, JavaScript, Bootstrap}}{}
          \resumeItemListStart
            \resumeItem{A Brisbane-based 'Library of Things' platform enabling members to borrow items with annual membership}
            \resumeItem{Built as part of DECO3801 course using Django, replacing third-party system limitations with a responsive, role-based web application}
            \resumeItem{Features include membership management, catalogue browsing, lending/returns, operating hours configuration, and admin dashboard.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{LULZ CLOUD} $|$ \emph{Spark, Cassandra, Docker, Nginx, PHP, Scala}}{}
          \resumeItemListStart
            \resumeItem{University of Queensland cloud computing project implementing a scalable web application using Cassandra NoSQL database, Spark Job Server for data processing, and Docker + Nginx for containerized deployment}
            \resumeItem{Awarded Project Excellence Award (Best Project Demo) by Prof Xue Li in Oct 2018.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd